---
title: "Homework 4"
author: "Shiyu Wang"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: yes
    toc: true
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Homework 4 vignette}
-->

# 5.8.2
Since $cond(A)=\frac{\sigma_{max}}{\sigma_min}$, the condition number a matrix is the ratio of its largest and smallest singular values.\
Generate required matrix X:
```{r}
X <- matrix(c(1, 100, 100, 1), 2, 2)
p <- c(0.5, 0.001)
```
Calculate condition number of matrix $X'X$:
```{r}
sgvals<- svd(t(X)%*%X)[["d"]]
max(sgvals)/min(sgvals)
```
Calculate the logistic variation of hessian matrix and its condition number
```{r}
h=t(X)%*%diag(p*(1-p))%*%X
sgvals_h<-svd(h)[["d"]]
max(sgvals_h)/min(sgvals_h)
```
Thus, in this case, the condition number of logistic variation hessian matrix is much larger than that of hessian matrix.


# 5.8.4
```{r}
irwls_glm<-function(X, y, family, maxit=25, tol=1e-10, lambda){
beta <- rep(0,ncol(X))
for(j in 1:maxit){
  b_old <- beta
  eta <- X %*% beta
  mu <- family$linkinv(eta)
  mu_p <- family$mu.eta(eta)
  z <- eta + (y - mu) / mu_p
  W <- as.numeric(mu_p^2 / family$variance(mu))
  XtX <- crossprod(X, diag(W) %*% X)
  Xtz <- crossprod(X, W * z)
  # Add the penalty (here get hints from Wengfeng Zhang, credits to him)
  V<-XtX+diag(lambda,dim(XtX)[1])
  beta<-solve(V, Xtz)
  if(sqrt(crossprod(beta - b_old)) < tol) break
}
beta
}
```
For problem 3 please refer to sparse_matrix.r in the R directory.

